Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-23 surfaces-write-up/surface-write-up.tex
added todo to move lemmas section
surfaces: delete random hanging 0
surfaces: some intro motivation rework

In part, this work is motivated by
of O'Dorney \cite{dorney:canonical}, who gives similar descriptions
of canonical rings for general $\bq$-divisors on $\bp^1$. For
particular $\bq$ divisors on stacky curves, the work by
Voight--Zureick-Brown \cite{vzb:stacky} and Landesman--Ruhm--Zhang
\cite{lrz:spin-cring} on log spin canonical rings provides
useful bounds on rings of modular forms of Fuchsian groups.

@@

\todo{Include summary of what each of the sections do.}0

\section{Lemmas for Generation and Relations}
\label{sec:lemmas}

>>>>

In part, this work is motivated by a recent paper by
O'Dorney \cite{dorney:canonical} who gives similar descriptions
of canonical rings for general $\bq$-divisors on $\bp^1$. This
study also has connections to the papers by Voight--Zureick-Brown 
\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring} on log 
spin canonical rings of particular $\bq$ divisors on stacky curves which 
provide bounds on rings of modular forms of Fuchsian groups.

@@

\todo{Include summary of what each of the sections do.}
\todo{Incorperate the following section into the pm section}
\section{Lemmas for Generation and Relations}
\label{sec:lemmas}
